Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-02-22 paper/main.tex
Completed referee's second suggestion, and also replaced journal names with aastex commands in the bibliography

Pulsars are rapidly rotating neutron stars, the sites of some of the highest energy physical processes in the universe, owing to the very strong gravitational and magnetic fields that surround them.
Discovered first via their lighthouse-like beam of radio emission \citep{Hewish1968}, which we detect as a series of regularly spaced pulses, it was quickly realised that the physics governing the relativistic plasma that generates this beam was not well understood---a state of affairs that persists to the present day \citep[e.g.][]{Melrose2021}.
The uniqueness of each pulsar's emission signature provides a wealth of information that can be used to test proposed emission mechanisms, and it has been proven again and again over the past several decades that in-depth studies of individual pulsars can provide valuable clues for understanding the population as a whole.
This, along with tests of general relativity \citep[e.g.][]{Kramer2006,Miao2021}, pulsar timing arrays for gravitational wave detection \citep[e.g.][]{Manchester2013}, pulsar braking and magnetospheric dynamics \citep[e.g.][]{Gao2017,Wang2020}, the neutron star equation of state \citep[e.g.][]{Demorest2010,Antoniadis2013,Pang2021}, and other pulsar science applications, motivates efforts to find new pulsars via large scale pulsar surveys, which continue to be conducted up to the present day.

@@

Pulsars with complicated drifting behavior, and which are bright enough for single pulse analysis, are relatively rare.
Even a cursory glance at the drift bands of \psr{} show that its drifting behaviour is indeed complex, making it a welcome addition to this category of pulsar.

@@

All of these complex drifting behaviors present a natural challenge to the carousel model, whose most basic formulation predicts only a single stable drifting mode, due to the expected stability of the underlying electric and magnetic fields that generate the carousel motion.
Nevertheless, many of the above effects can be successfully explained with the carousel model by invoking aliasing effects that arise due to beating between the stellar rotation rate and the carousel's rotation.
In the presence of aliasing, multiple drift modes can be explained if the number of sparks in the carousel changes, even if the carousel speed itself doesn't change.
This idea has been invoked to explain the multiple drift rates of B1918$+$19 \citep{Rankin2013}, B1819$-$22 \citep{Joshi2017,Janagal2021}, and B0031$-$07 \citep{McSweeney2019a}.
Aliasing can also ``amplify'' the variability of the drift rate if the ratio of stellar rotation and carousel rotation is very close to a ratio of small integers.
That is, a small change in the magnetospheric conditions near the stellar surface (where the sparks reside) can appear to the observer as a relatively large change in the drift rate.
\citet{VanLeeuwen2012} elucidated the connection between the accelerating potential within the polar gap and the carousel behavior, and found that the variability of B0826$-$34's drift rate can be explained in this way.

>>>>

Pulsars are rapidly rotating neutron stars, the sites of some of the highest energy physical processes in the universe, owing to the very strong gravitational and magnetic fields that surround them.
Discovered first via their lighthouse-like beam of radio emission \citep{Hewish1968}, which we detect as a series of regularly spaced pulses, it was quickly realised that the physics governing the relativistic plasma that generates this beam was not well understood---a state of affairs that persists to the present day \citep[e.g.][]{Melrose2021}.
The uniqueness of each pulsar's emission signature provides a wealth of information that can be used to test proposed emission mechanisms, and it has been proven again and again over the past several decades that in-depth studies of individual pulsars can provide valuable clues for understanding the population as a whole.
{\bf
This, along with tests of general relativity \citep[e.g.][]{Kramer2006,Miao2021}, pulsar timing arrays for gravitational wave detection \citep[e.g.][]{Manchester2013}, pulsar braking and magnetospheric dynamics \citep[e.g.][]{Gao2017,Wang2020}, the neutron star equation of state \citep[e.g.][]{Demorest2010,Antoniadis2013,Pang2021}, and other pulsar science applications, motivates efforts to find new pulsars via large scale pulsar surveys, which continue to be conducted up to the present day.
}

@@

Pulsars with complicated drifting behavior, and which are bright enough for single pulse analysis, are relatively rare.
Even a cursory glance at the drift bands of \psr{} show that its drifting behaviour is indeed complex, making it a welcome addition to this category of pulsar.
{\bf 
\psr{} is also found to contain null sequences, a phenomenon which is known to be connected to drifting behaviour, originally noticed by \citep{Lyne1983}, and further attested by recent studies of PSRs J1727$-$2739 \citep{Wen2016}, J1822$-$2256 \citep{Janagal2022}, and the Vela pulsar \citep{Wen2020}.
}

@@

All of these complex drifting behaviors present a natural challenge to the carousel model, whose most basic formulation predicts only a single stable drifting mode, due to the expected stability of the underlying electric and magnetic fields that generate the carousel motion.
Nevertheless, many of the above effects can be successfully explained with the carousel model by invoking aliasing effects that arise due to beating between the stellar rotation rate and the carousel's rotation.
In the presence of aliasing, multiple drift modes can be explained if the number of sparks in the carousel changes, even if the carousel speed itself doesn't change.
This idea has been invoked to explain the multiple drift rates of B1918$+$19 \citep{Rankin2013}, B1819$-$22 \citep{Joshi2017,Janagal2022}, and B0031$-$07 \citep{McSweeney2019a}.
Aliasing can also ``amplify'' the variability of the drift rate if the ratio of stellar rotation and carousel rotation is very close to a ratio of small integers.
That is, a small change in the magnetospheric conditions near the stellar surface (where the sparks reside) can appear to the observer as a relatively large change in the drift rate.
\citet{VanLeeuwen2012} elucidated the connection between the accelerating potential within the polar gap and the carousel behavior, and found that the variability of B0826$-$34's drift rate can be explained in this way.
